---
title: "Assignment5"
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

## Instructions: Please read through this before you begin 

## Load packages 

To start, load all the required packages with the following code. Install them if they are not installed yet.

```{r, message=FALSE}
library(tidyverse)
library(knitr)
```

<p>&nbsp;</p>
## Exercise 1. Tibble and Data Import
Import the data frames listed below into R and parse the columns appropriately when needed. Watch out for the formatting oddities of each dataset. Print the results directly, without using kable().

You only need to finish any three out of the five questions in this exercise in order to get credit.
<p>&nbsp;</p>

##### 1.1 Create the following tibble manually, first using tribble() and then using tibble(). Print both results. [We didn’t have time to cover this in class, but look up how these functions work here]

```{r}
tribble(
  ~a, ~b, ~c,
  #--|--|----
  1, 2.1, "apple",
  2, 3.2, "orange"
)
```
```{r}
c1<-as.integer(1:2)
c2<-c(2.1,3.2)
c3<-c("apple","orange")
d<-data.frame(c1,c2,c3)
as.tibble(d)
```
##### 1.2 Import https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/dataset2.txt into R. Change the column names into “Name”, “Weight”, “Price”.
```{r}
c3<-c("Name","Weight","Price")
d2<-read_csv("https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/dataset2.txt",col_names = c3)
as.tibble(d2)


```

##### 1.3 Import https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/dataset3.txt into R. Watch out for the first few lines, missing values, separators, quotation marks, and deliminaters.
```{r}
d3<-read_csv("https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/dataset3.txt",locale(decimal_mark = "; /"))
d3
```

